\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-08 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
adding IEEE 14 bus sim results

\subsubsection{Contributions of this paper}
Our main contribution is to demonstrate that by harnessing recent developments in generalized gradient flows \cite{ambrosio2008gradient} and proximal algorithms \cite{parikh2014proximal}, it is possible to perform \emph{nonparametric} propagation of the joint state PDFs subject to the stochastic nonlinear dynamics of a networked power system, and that the computation can be performed in a gridless and scalable manner.

@@

Fig. \ref{fig:IEEE14marginals} shows the time snapshots of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs for generator $i=1,\hdots, n=5$, computed using the weighted point clouds $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$. Notice that in Fig. \ref{fig:IEEE14marginals}, the horizontal axes of the subfigures have periodic boundary conditions, i.e., $(\theta_{i},\omega_{i})\in\mathbb{T}\times\mathbb{R}$ (cylinder). Fig. \ref{fig:CompTimeIEEE14bus} shows the computational times needed to update $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ via the Euler-Maruyama and the Algorithm \ref{algo:KineticProx}.

>>>>

\subsubsection{Contributions of this paper}
Our main contribution is to demonstrate that by harnessing recent developments in generalized gradient flows \cite{ambrosio2008gradient} and proximal algorithms \cite{parikh2014proximal}, it is possible to perform \emph{nonparametric} propagation of the joint state PDFs subject to the stochastic nonlinear dynamics of a networked power system, and that the computation can be performed in a gridless and scalable manner. In doing so, the paper also makes theoretical contribution by introducing a change of coordinates that transforms the joint PDF evolution equations in way that is amenable for the aforesaid generalized proximal recursions.

@@

Fig. \ref{fig:IEEE14marginals} shows the time snapshots of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs for generator $i=1,\hdots, n=5$, computed using the weighted point clouds $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$. Notice that in Fig. \ref{fig:IEEE14marginals}, the horizontal axes of the subfigures have periodic boundary conditions, i.e., $(\theta_{i},\omega_{i})\in\mathbb{T}\times\mathbb{R}$ (cylinder). Fig. \ref{fig:CompTimeIEEE14bus} shows the computational times needed to update $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ via the algorithm in Sec.  \ref{sec:ProxAlgo}.
